### 2021-10-13 content/80.formal-definition.tex
more \# magic

The domain of discourse $\mathbb{D}$ is the set of $\mathbb{IRI}$ identifiers \cite{doi:10.17487/rfc3987} (notation $\texttt{<http://example.com/>}$)\footnote{
    For simplicity, blank nodes are not included in this formalisation, as RO-Crate
    recommends the use of IRI identifiers: \url{https://www.researchobject.org/ro-crate/1.1/appendix/jsonld.html#describing-entities-in-json-ld}
}, with additional descriptions using numbers $\mathbb{R}$ (notation $13.37$) and literal strings $\mathbb{S}$ (notation $\text{“Hello”}$).

>>>>

The domain of discourse $\mathbb{D}$ is the set of $\mathbb{IRI}$ identifiers \cite{doi:10.17487/rfc3987} (notation $\texttt{<http://example.com/>}$)\footnote{
    For simplicity, blank nodes are not included in this formalisation, as RO-Crate
    recommends the use of IRI identifiers: \url{https://www.researchobject.org/ro-crate/1.1/appendix/jsonld.html\#describing-entities-in-json-ld}
}, with additional descriptions using numbers $\mathbb{R}$ (notation $13.37$) and literal strings $\mathbb{S}$ (notation $\text{“Hello”}$).
